\documentclass[11pt,a4paper,sans]{moderncv}

% Theme and colors
\moderncvstyle{banking}
\moderncvcolor{blue}

% Adjust page margins
\usepackage[scale=0.9]{geometry}
\setlength{\hintscolumnwidth}{3cm}

% Personal info
\firstname{Anjo}
\familyname{Tadena}
\title{Fullstack Developer}
\phone{+63 997 982 3698}
\email{tadena.anjo@gmail.com}
\homepage{anjotadena.vercel.app}
\social[linkedin]{linkedin.com/in/anjotadena}
\social[github]{github.com/anjotadena}
\extrainfo{Cebu, Philippines}

\begin{document}
\makecvtitle

% ----- WORK EXPERIENCE -----
\section{Work Experience}

\cventry{Dec 2023 -- Present}{Senior Software Engineer}{Nelnet Philippines Inc.}{Manila}{}{
\begin{itemize}
  \item Led a team in building an in-house Human Resource Management System (HRMS) while delivering scalable applications for Nelnet Business Services.
  \item Built full-stack solutions using ASP.NET Core, Angular, and microservices-based architecture.
  \item Leveraged AWS and Azure cloud services for serverless, containerized, and CI/CD pipeline solutions.
  \item Mentored team members, conducted code reviews, and guided adoption of best practices.
  \item Championed DevOps practices, improving deployment reliability and reducing delivery cycle times.
\end{itemize}}

\cventry{May 2023 -- Oct 2023}{Senior Software Engineer}{Prosource BPO}{Manila}{}{
\begin{itemize}
  \item Guided a distributed team maintaining and enhancing enterprise client products using C\#, Angular, Azure, VueJS, and Ionic.
  \item Collaborated with Product Owner to align business goals with technical deliverables.
  \item Introduced CI/CD improvements and DevOps practices to accelerate delivery.
  \item Oversaw design and development of new features while maintaining high product quality.
\end{itemize}}

\cventry{Mar 2022 -- Mar 2023}{Software Engineer}{Arcanys / XLR8 Hub Inc.}{Cebu}{}{
\begin{itemize}
  \item Led development team for client projects, using ReactJS front-end and ASP.NET Core back-end.
  \item Acted as primary liaison with client stakeholders for requirements and delivery updates.
  \item Introduced coding standards, best practices, and technical documentation processes.
  \item Fostered collaboration between designers, QA, and developers for seamless product integration.
\end{itemize}}

\cventry{Aug 2019 -- Mar 2022}{Software Engineer}{Sprobe Inc.}{Cebu}{}{
\begin{itemize}
  \item Directed a small team to deliver systems for Japanese and Singaporean clients.
  \item Utilized ReactJS, ASP.NET Core, and cloud-native approaches for robust, scalable systems.
  \item Drove best practices in testing, reviews, and architecture.
  \item Coordinated cross-functional collaboration with designers, PMs, and testers.
\end{itemize}}

\cventry{Jan 2016 -- Aug 2019}{Software Engineer}{Code Republic / Ark Creative Studio}{Cebu}{}{
\begin{itemize}
  \item Delivered scalable web/mobile applications using ReactJS, NodeJS, Laravel, Angular, and serverless technologies.
  \item Worked directly with clients, translating business requirements into technical solutions.
  \item Produced documentation and maintained high coding standards.
\end{itemize}}

\cventry{Apr 2015 -- Aug 2015}{Software Engineer}{Central Mindanao University}{Mindanao}{}{
\begin{itemize}
  \item Designed and developed the Library System for Research and Thesis Management using VueJS (front-end) and Laravel (back-end).
  \item Implemented duplicate detection and optimized schema for large-scale academic research.
  \item Trained end users and deployed across university departments.
\end{itemize}}

% ----- EDUCATION -----
\section{Education}
\cventry{2010 -- 2014}{Bachelor of Science in Information Technology}{Central Mindanao University}{Mindanao}{}{}

% ----- SKILLS -----
\section{Skills}
\cvitem{}{C\#, ASP.NET Core, TSQL, MVC, Blazor, Angular, ReactJS, VueJS, TypeScript, Docker, Azure Services, AWS, Microservices, MongoDB, MS SQL, DevOps, CI/CD, Cloud Architecture}


\end{document}
